### 2019-02-18 sections/contributions.tex
merge old and new intros
fixes in 1.4

\subsection{Contributions}

@@

We present a calculus for modelling declarative workflows, embedded in a simply typed lambda-calculus.
We develop an operational semantics that is driven by user inputs.
The semantics of the task language is clearly separated from the semantics of the underlying host language.
Along the semantics, we present the following semantic observations on tasks: the current value, whether a term is stuck, the current user interface, and the accepted inputs.
%%NOTE: iTasks things are moved to related work
% All these observations exist in iTasks, albeit combined into one big type.
By separating them in the style of a deep embedding \cite{conf/cefp/Gibbons13}, we make explicit where and where not, they depend on each other.

>>>>

@@

We present a calculus for modelling declarative workflows, embedded in a simply typed lambda-calculus.
We develop an operational semantics that is driven by user inputs.
The semantics of the task language is clearly separated from the semantics of the underlying host language.
Along with the semantics, we present the following semantic observations on tasks: the current value, whether a term is stuck, the current user interface, and the accepted inputs.
\fixme{we do not provide observation for user interface!}
%%NOTE: iTasks things are moved to related work
% All these observations exist in iTasks, albeit combined into one big type.
By separating them in the style of a deep embedding \cite{conf/cefp/Gibbons13}, we make explicit where and where not, they depend on each other.

### 2019-02-18 sections/introduction.tex
fixes in 1.4

In this paper we tend to identify the essence of \TOP in formal as well as an informal way.
These core principles lead to a formal system for \TOP called \TOPHAT.
\TOPHAT paves the way to formal reasoning about applications written using the \TOP paradigm,
like those in \ITASKS and \MTASKS.

\TOP applications give rise to concepts like concurrency, synchronisation, \GUI-programming and program generation.
In this paper we identify common concepts with already existing languages and frameworks,
and describe their similarities and differences.

@@

  \item
    We informally describe the essential concepts of task-oriented programming (\TOP).
    We have a strong focus on modelling using collaboration
    while keeping a constant desire to rapidly generate executable applications into account.

  \item
    We present a formal calculus for \TOP, arising naturally from above essential concepts.
    Hereby we provide ground work to apply formal reasoning about \TOP specifications in future work.

  \item
    Using both informal and formal descriptions, we compare \TOP and \TOPHAT with multiple related work in the area,
    ranging from business process modelling languages, to process algebras and reactive programming frameworks.

>>>>

In this paper we aim to identify the essence of \TOP in formal as well as an informal way.
These core principles lead to a formal system for \TOP called \TOPHAT.
\TOPHAT paves the way to formal reasoning about applications written using the \TOP paradigm,
like those in \ITASKS and \MTASKS.

\TOP applications give rise to concepts like concurrency, synchronisation, \GUI-programming and program generation.
In this paper we identify common concepts from already existing languages and frameworks,
and describe their similarities and differences.\fixme{What do you mean with this sentence?}

@@

  \item
    We informally describe the essential concepts of task-oriented programming (\TOP).
    \TOP has a strong focus on modelling using collaboration
    while keeping a constant desire to rapidly generate executable applications into account.

  \item
    We present a formal calculus for \TOP, arising naturally from the aforementioned essential concepts.
    In doing so, we lay the ground work to allow formal reasoning about \TOP specifications in future work.

  \item
    Using both informal and formal descriptions, we compare \TOP and \TOPHAT with multiple related works in the areas,
    ranging from business process modelling languages, to process algebras and reactive programming frameworks.
